---
title: "Environmental Data"
output:
  html_document: default
  html_notebook: default
---

Load Variables:
`GT8134017	GT8134022	GT8134027	GT8134028	GT8153030	GT8153031	GT8172035	GT8172037`

```{r dataload,message=FALSE}
require(NNS)

environmental.data=read.csv("https://raw.githubusercontent.com/OVVO-Financial/Environmental-Forecasting/master/Data/GWL_Final_data.csv",sep = ',',header = TRUE)

GT8134017=environmental.data[,"GT8134017"]
GT8134022=environmental.data[,"GT8134022"]
GT8134027=environmental.data[,"GT8134027"]
GT8134028=environmental.data[,"GT8134028"]
GT8153030=environmental.data[,"GT8153030"]
GT8153031=environmental.data[,"GT8153031"]
GT8172035=environmental.data[,"GT8172035"]
GT8172037=environmental.data[,"GT8172037"]
```

# Create our evaluation formula `NSE`

```{r NSE}
NSE=function(x,y){
  NSE=1- (sum((x-y)^2)/sum((y-mean(y))^2))
  return(NSE)
}
```


#1. Forecasts for `GT8134017`
View our data and determine our seasonality.
```{r plots}
plot(GT8134017,type='l')
```

Since we are dealing with highly periodic monthly data, we will use a default of `seasonal.factor=12` and sequentially add other multiples of 12 to incorporate longer term effects.

We test our linear method for comparitive statistics purposes and then decide on an acceptable `seasonal.factor`.  Generally, I like to test on a period double the anticipated forecast period.

##1.1 12 Month Out of Sample Forecast

```{r data1}
# Create a training set
GT8134017_12.train=GT8134017[1:348]

# Create a test set
GT8134017_12.test=GT8134017[349:372]

nns.GT8134017_12=NNS.ARMA(GT8134017_12.train,h=24,seasonal.factor = 12,method='lin', plot = FALSE)

nns.GT8134017_12.24=NNS.ARMA(GT8134017_12.train,h=24,seasonal.factor = c(12,24),method='lin', plot = FALSE)

nns.GT8134017_12.24.36=NNS.ARMA(GT8134017_12.train,h=24,seasonal.factor = c(12,24,36),method='lin', plot = FALSE)

nns.GT8134017_12.24.36.48=NNS.ARMA(GT8134017_12.train,h=24,seasonal.factor = c(12,24,36,48),method='lin', plot = FALSE)

nns.GT8134017_12.24.36.48.60=NNS.ARMA(GT8134017_12.train,h=24,seasonal.factor = c(12,24,36,48,60),method='lin', plot = FALSE)

nns.GT8134017_12.24.36.48.60.72=NNS.ARMA(GT8134017_12.train,h=24,seasonal.factor = c(12,24,36,48,60,72),method='lin', plot = FALSE)

nns.GT8134017_12.24.36.48.60.72.84=NNS.ARMA(GT8134017_12.train,h=24,seasonal.factor = c(12,24,36,48,60,72,84),method='lin', plot = FALSE)

# SSE 12
sum((nns.GT8134017_12-GT8134017_12.test)^2)

# SSE 24
sum((nns.GT8134017_12.24-GT8134017_12.test)^2)

# SSE 36
sum((nns.GT8134017_12.24.36-GT8134017_12.test)^2)

# SSE 48
sum((nns.GT8134017_12.24.36.48-GT8134017_12.test)^2)

# SSE 60
sum((nns.GT8134017_12.24.36.48.60-GT8134017_12.test)^2)

# SSE 72
sum((nns.GT8134017_12.24.36.48.60.72-GT8134017_12.test)^2)

# SSE 84
sum((nns.GT8134017_12.24.36.48.60.72.84-GT8134017_12.test)^2)
```

So the combination of periods 12 and 24 yielded our lowest linear `SSE`.  Let's now incorporate the nonlinear regression with our linear estimate by setting `method='both'`.

```{r data1a}
# Incorporate nonlinearity
nns.GT8134017_12.24=NNS.ARMA(GT8134017_12.train,h=24,seasonal.factor = c(12,24),method='both', plot = FALSE)

# SSE
sum((nns.GT8134017_12.24-GT8134017_12.test)^2)
```

A drastic reduction in `SSE`.  Finally, let's isolate the nonlinear regression to determine whether it has better explanatory power alone.  We set `method='nonlin'`.

```{r data1aa}
# Isolate nonlinearity
nns.GT8134017_12.24=NNS.ARMA(GT8134017_12.train,h=24,seasonal.factor = c(12,24),method='nonlin', plot = FALSE)

# SSE
sum((nns.GT8134017_12.24-GT8134017_12.test)^2)
```
No, it does not.  Our final section is for `seasonal.factor=c(12,24)` and `method='both'`, using our full `GT8134017` dataset with a `training.set=372`.

```{r data1full}
nns.GT8134017_12.24_12=NNS.ARMA(GT8134017,training.set=372,h=12,seasonal.factor = c(12,24),method='both')

# SSE
sum((nns.GT8134017_12.24_12-tail(GT8134017,12))^2)

# NSE Statistic
NSE(nns.GT8134017_12.24_12,tail(GT8134017,12))
```


##1.2 24 Month Out of Sample Forecast
We now repeat the above parameter identification procedure for `h=24`.

```{r data1_24}
# Create a training set
GT8134017_24.train=GT8134017[1:312]

# Create a test set
GT8134017_24.test=GT8134017[313:360]

nns.GT8134017_12=NNS.ARMA(GT8134017_24.train,h=48,seasonal.factor = 12,method='lin', plot = FALSE)

nns.GT8134017_12.24=NNS.ARMA(GT8134017_24.train,h=48,seasonal.factor = c(12,24),method='lin', plot = FALSE)

nns.GT8134017_12.24.36=NNS.ARMA(GT8134017_24.train,h=48,seasonal.factor = c(12,24,36),method='lin', plot = FALSE)

nns.GT8134017_12.24.36.48=NNS.ARMA(GT8134017_24.train,h=48,seasonal.factor = c(12,24,36,48),method='lin', plot = FALSE)

nns.GT8134017_12.24.36.48.60=NNS.ARMA(GT8134017_24.train,h=48,seasonal.factor = c(12,24,36,48,60),method='lin', plot = FALSE)

nns.GT8134017_12.24.36.48.60.72=NNS.ARMA(GT8134017_24.train,h=48,seasonal.factor = c(12,24,36,48,60,72),method='lin', plot = FALSE)


# SSE 12
sum((nns.GT8134017_12-GT8134017_24.test)^2)

# SSE 24
sum((nns.GT8134017_12.24-GT8134017_24.test)^2)

# SSE 36
sum((nns.GT8134017_12.24.36-GT8134017_24.test)^2)

# SSE 48
sum((nns.GT8134017_12.24.36.48-GT8134017_24.test)^2)

# SSE 60
sum((nns.GT8134017_12.24.36.48.60-GT8134017_24.test)^2)

# SSE 72
sum((nns.GT8134017_12.24.36.48.60.72-GT8134017_24.test)^2)


# Incorporate nonlinearity
nns.GT8134017_12.24.36.48.60.72=NNS.ARMA(GT8134017_24.train,h=48,seasonal.factor = c(12,24,36,48,60,72),method='both', plot = FALSE)

# SSE 72 both
sum((nns.GT8134017_12.24.36.48.60.72-GT8134017_24.test)^2)

# Isolate nonlinearity
nns.GT8134017_12.24.36.48.60.72=NNS.ARMA(GT8134017_24.train,h=48,seasonal.factor = c(12,24,36,48,60,72),method='nonlin', plot = FALSE)

# SSE 72 nonlin
sum((nns.GT8134017_12.24.36.48.60.72-GT8134017_24.test)^2)

```

We really benefit from using the nonlinear method exclusively for `h=24` forecast period.


```{r data1_24b}
nns.GT8134017_12.24.36.48.60.72_24=NNS.ARMA(GT8134017,h=24,training.set = 360,seasonal.factor = c(12,24,36,48,60,72),method='nonlin')

# SSE
sum((nns.GT8134017_12.24.36.48.60.72_24-tail(GT8134017,24))^2)

# NSE Statistic
NSE(nns.GT8134017_12.24.36.48.60.72_24,tail(GT8134017,24))
```

We will now perform the same analysis for the remaining variables.


#2. Forecasts for `GT8134022`
View our data.
```{r plots2}
plot(GT8134022,type='l')
```

##2.1 12 Month Out of Sample Forecast
```{r data2}
# Create a training set
GT8134022_12.train=GT8134022[1:348]

# Create a test set
GT8134022_12.test=GT8134022[349:372]

nns.GT8134022_12=NNS.ARMA(GT8134022_12.train,h=24,seasonal.factor = 12,method='lin', plot = FALSE)

nns.GT8134022_12.24=NNS.ARMA(GT8134022_12.train,h=24,seasonal.factor = c(12,24),method='lin', plot = FALSE)

nns.GT8134022_12.24.36=NNS.ARMA(GT8134022_12.train,h=24,seasonal.factor = c(12,24,36),method='lin', plot = FALSE)

nns.GT8134022_12.24.36.48=NNS.ARMA(GT8134022_12.train,h=24,seasonal.factor = c(12,24,36,48),method='lin', plot = FALSE)

nns.GT8134022_12.24.36.48.60=NNS.ARMA(GT8134022_12.train,h=24,seasonal.factor = c(12,24,36,48,60),method='lin', plot = FALSE)

nns.GT8134022_12.24.36.48.60.72=NNS.ARMA(GT8134022_12.train,h=24,seasonal.factor = c(12,24,36,48,60,72),method='lin', plot = FALSE)

nns.GT8134022_12.24.36.48.60.72.84=NNS.ARMA(GT8134022_12.train,h=24,seasonal.factor = c(12,24,36,48,60,72,84),method='lin', plot = FALSE)

# SSE 12
sum((nns.GT8134022_12-GT8134022_12.test)^2)

# SSE 24
sum((nns.GT8134022_12.24-GT8134022_12.test)^2)

# SSE 36
sum((nns.GT8134022_12.24.36-GT8134022_12.test)^2)

# SSE 48
sum((nns.GT8134022_12.24.36.48-GT8134022_12.test)^2)

# SSE 60
sum((nns.GT8134022_12.24.36.48.60-GT8134022_12.test)^2)

# SSE 72
sum((nns.GT8134022_12.24.36.48.60.72-GT8134022_12.test)^2)

# SSE 84
sum((nns.GT8134022_12.24.36.48.60.72.84-GT8134022_12.test)^2)
```

```{r data2a}
# Incorporate nonlinearity
nns.GT8134022_12.24=NNS.ARMA(GT8134022_12.train,h=24,seasonal.factor = c(12,24),method='both', plot = FALSE)

# SSE 24
sum((nns.GT8134022_12.24-GT8134022_12.test)^2)

# Isolate nonlinearity
nns.GT8134022_12.24=NNS.ARMA(GT8134022_12.train,h=24,seasonal.factor = c(12,24),method='nonlin', plot = FALSE)

# SSE 24
sum((nns.GT8134022_12.24-GT8134022_12.test)^2)
```

```{r data2full}
nns.GT8134022_12.24_12=NNS.ARMA(GT8134022,training.set=372,h=12,seasonal.factor = c(12,24),method='both')

# SSE 24
sum((nns.GT8134022_12.24_12-tail(GT8134022,12))^2)

# NSE Statistic
NSE(nns.GT8134022_12.24_12,tail(GT8134022,12))
```

##2.2 24 Month Out of Sample Forecast
```{r data2_24}
# Create a training set
GT8134022_24.train=GT8134022[1:312]

# Create a test set
GT8134022_24.test=GT8134022[313:360]

nns.GT8134022_12=NNS.ARMA(GT8134022_24.train,h=48,seasonal.factor = 12,method='lin', plot = FALSE)

nns.GT8134022_12.24=NNS.ARMA(GT8134022_24.train,h=48,seasonal.factor = c(12,24),method='lin', plot = FALSE)

nns.GT8134022_12.24.36=NNS.ARMA(GT8134022_24.train,h=48,seasonal.factor = c(12,24,36),method='lin', plot = FALSE)

nns.GT8134022_12.24.36.48=NNS.ARMA(GT8134022_24.train,h=48,seasonal.factor = c(12,24,36,48),method='lin', plot = FALSE)

nns.GT8134022_12.24.36.48.60=NNS.ARMA(GT8134022_24.train,h=48,seasonal.factor = c(12,24,36,48,60),method='lin', plot = FALSE)

nns.GT8134022_12.24.36.48.60.72=NNS.ARMA(GT8134022_24.train,h=48,seasonal.factor = c(12,24,36,48,60,72),method='lin', plot = FALSE)


# SSE 12
sum((nns.GT8134022_12-GT8134022_24.test)^2)

# SSE 24
sum((nns.GT8134022_12.24-GT8134022_24.test)^2)

# SSE 36
sum((nns.GT8134022_12.24.36-GT8134022_24.test)^2)

# SSE 48
sum((nns.GT8134022_12.24.36.48-GT8134022_24.test)^2)

# SSE 60
sum((nns.GT8134022_12.24.36.48.60-GT8134022_24.test)^2)

# SSE 72
sum((nns.GT8134022_12.24.36.48.60.72-GT8134022_24.test)^2)


# Incorporate nonlinearity
nns.GT8134022_12.24.36.48=NNS.ARMA(GT8134022_24.train,h=48,seasonal.factor = c(12,24,36,48),method='both', plot = FALSE)

# SSE 48 both
sum((nns.GT8134022_12.24.36.48-GT8134022_24.test)^2)

# Isolate nonlinearity
nns.GT8134022_12.24.36.48=NNS.ARMA(GT8134022_24.train,h=48,seasonal.factor = c(12,24,36,48),method='nonlin', plot = FALSE)

# SSE 48 nonlin
sum((nns.GT8134022_12.24.36.48-GT8134022_24.test)^2)
```

```{r data2_24b}
nns.GT8134022_12.24.36.48_24=NNS.ARMA(GT8134022,h=24,training.set = 360,seasonal.factor = c(12,24,36,48),method='both')

# SSE 48
sum((nns.GT8134022_12.24.36.48_24-tail(GT8134022,24))^2)

# NSE Statistic
NSE(nns.GT8134022_12.24.36.48_24,tail(GT8134022,24))
```


#3. Forecasts for `GT8134027`
View our data.
```{r plots3}
plot(GT8134027,type='l')
```

##3.1 12 Month Out of Sample Forecast
```{r data3}
# Create a training set
GT8134027_12.train=GT8134027[1:348]

# Create a test set
GT8134027_12.test=GT8134027[349:372]

nns.GT8134027_12=NNS.ARMA(GT8134027_12.train,h=24,seasonal.factor = 12,method='lin', plot = FALSE)

nns.GT8134027_12.24=NNS.ARMA(GT8134027_12.train,h=24,seasonal.factor = c(12,24),method='lin', plot = FALSE)

nns.GT8134027_12.24.36=NNS.ARMA(GT8134027_12.train,h=24,seasonal.factor = c(12,24,36),method='lin', plot = FALSE)

nns.GT8134027_12.24.36.48=NNS.ARMA(GT8134027_12.train,h=24,seasonal.factor = c(12,24,36,48),method='lin', plot = FALSE)

nns.GT8134027_12.24.36.48.60=NNS.ARMA(GT8134027_12.train,h=24,seasonal.factor = c(12,24,36,48,60),method='lin', plot = FALSE)

nns.GT8134027_12.24.36.48.60.72=NNS.ARMA(GT8134027_12.train,h=24,seasonal.factor = c(12,24,36,48,60,72),method='lin', plot = FALSE)

nns.GT8134027_12.24.36.48.60.72.84=NNS.ARMA(GT8134027_12.train,h=24,seasonal.factor = c(12,24,36,48,60,72,84),method='lin', plot = FALSE)

# SSE 12
sum((nns.GT8134027_12-GT8134027_12.test)^2)

# SSE 24
sum((nns.GT8134027_12.24-GT8134027_12.test)^2)

# SSE 36
sum((nns.GT8134027_12.24.36-GT8134027_12.test)^2)

# SSE 48
sum((nns.GT8134027_12.24.36.48-GT8134027_12.test)^2)

# SSE 60
sum((nns.GT8134027_12.24.36.48.60-GT8134027_12.test)^2)

# SSE 72
sum((nns.GT8134027_12.24.36.48.60.72-GT8134027_12.test)^2)

# SSE 84
sum((nns.GT8134027_12.24.36.48.60.72.84-GT8134027_12.test)^2)
```

```{r data3a}
# Incorporate nonlinearity
nns.GT8134027_12.24=NNS.ARMA(GT8134027_12.train,h=24,seasonal.factor = c(12,24),method='both', plot = FALSE)

# SSE 24
sum((nns.GT8134027_12.24-GT8134027_12.test)^2)

# Isolate nonlinearity
nns.GT8134027_12.24=NNS.ARMA(GT8134027_12.train,h=24,seasonal.factor = c(12,24),method='nonlin', plot = FALSE)

# SSE 24
sum((nns.GT8134027_12.24-GT8134027_12.test)^2)
```

```{r data3full}
nns.GT8134027_12.24_12=NNS.ARMA(GT8134027,training.set=372,h=12,seasonal.factor = c(12,24),method='both')

#SSE 24
sum((nns.GT8134027_12.24_12-tail(GT8134027,12))^2)

# NSE Statistic
NSE(nns.GT8134027_12.24_12,tail(GT8134027,12))
```

##3.2 24 Month Out of Sample Forecast
```{r data3_24}
# Create a training set
GT8134027_24.train=GT8134027[1:312]

# Create a test set
GT8134027_24.test=GT8134027[313:360]

nns.GT8134027_12=NNS.ARMA(GT8134027_24.train,h=48,seasonal.factor = 12,method='lin', plot = FALSE)

nns.GT8134027_12.24=NNS.ARMA(GT8134027_24.train,h=48,seasonal.factor = c(12,24),method='lin', plot = FALSE)

nns.GT8134027_12.24.36=NNS.ARMA(GT8134027_24.train,h=48,seasonal.factor = c(12,24,36),method='lin', plot = FALSE)

nns.GT8134027_12.24.36.48=NNS.ARMA(GT8134027_24.train,h=48,seasonal.factor = c(12,24,36,48),method='lin', plot = FALSE)

nns.GT8134027_12.24.36.48.60=NNS.ARMA(GT8134027_24.train,h=48,seasonal.factor = c(12,24,36,48,60),method='lin', plot = FALSE)

nns.GT8134027_12.24.36.48.60.72=NNS.ARMA(GT8134027_24.train,h=48,seasonal.factor = c(12,24,36,48,60,72),method='lin', plot = FALSE)


# SSE 12
sum((nns.GT8134027_12-GT8134027_24.test)^2)

# SSE 24
sum((nns.GT8134027_12.24-GT8134027_24.test)^2)

# SSE 36
sum((nns.GT8134027_12.24.36-GT8134027_24.test)^2)

# SSE 48
sum((nns.GT8134027_12.24.36.48-GT8134027_24.test)^2)

# SSE 60
sum((nns.GT8134027_12.24.36.48.60-GT8134027_24.test)^2)

# SSE 72
sum((nns.GT8134027_12.24.36.48.60.72-GT8134027_24.test)^2)


# Incorporate nonlinearity
nns.GT8134027_12.24.36.48.60=NNS.ARMA(GT8134027_24.train,h=48,seasonal.factor = c(12,24,36,48,60),method='both', plot = FALSE)

# SSE 60 both
sum((nns.GT8134027_12.24.36.48.60-GT8134027_24.test)^2)

# Isolate nonlinearity
nns.GT8134027_12.24.36.48.60=NNS.ARMA(GT8134027_24.train,h=48,seasonal.factor = c(12,24,36,48,60),method='nonlin', plot = FALSE)

# SSE 60 nonlin
sum((nns.GT8134027_12.24.36.48.60-GT8134027_24.test)^2)

```

```{r data3_24b}
nns.GT8134027_12.24.36.48.60_24=NNS.ARMA(GT8134027,h=24,training.set = 360,seasonal.factor = c(12,24,36,48,60),method='nonlin')

# SSE 60
sum((nns.GT8134027_12.24.36.48.60_24-tail(GT8134027,24))^2)

# NSE Statistic
NSE(nns.GT8134027_12.24.36.48.60_24,tail(GT8134027,24))
```




#4. Forecasts for `GT8134028`
View our data.
```{r plots4}
plot(GT8134028,type='l')
```

##4.1 12 Month Out of Sample Forecast
```{r data4}
# Create a training set
GT8134028_12.train=GT8134028[1:348]

# Create a test set
GT8134028_12.test=GT8134028[349:372]

nns.GT8134028_12=NNS.ARMA(GT8134028_12.train,h=24,seasonal.factor = 12,method='lin', plot = FALSE)

nns.GT8134028_12.24=NNS.ARMA(GT8134028_12.train,h=24,seasonal.factor = c(12,24),method='lin', plot = FALSE)

nns.GT8134028_12.24.36=NNS.ARMA(GT8134028_12.train,h=24,seasonal.factor = c(12,24,36),method='lin', plot = FALSE)

nns.GT8134028_12.24.36.48=NNS.ARMA(GT8134028_12.train,h=24,seasonal.factor = c(12,24,36,48),method='lin', plot = FALSE)

nns.GT8134028_12.24.36.48.60=NNS.ARMA(GT8134028_12.train,h=24,seasonal.factor = c(12,24,36,48,60),method='lin', plot = FALSE)

nns.GT8134028_12.24.36.48.60.72=NNS.ARMA(GT8134028_12.train,h=24,seasonal.factor = c(12,24,36,48,60,72),method='lin', plot = FALSE)

nns.GT8134028_12.24.36.48.60.72.84=NNS.ARMA(GT8134028_12.train,h=24,seasonal.factor = c(12,24,36,48,60,72,84),method='lin', plot = FALSE)

# SSE 12
sum((nns.GT8134028_12-GT8134028_12.test)^2)

# SSE 24
sum((nns.GT8134028_12.24-GT8134028_12.test)^2)

# SSE 36
sum((nns.GT8134028_12.24.36-GT8134028_12.test)^2)

# SSE 48
sum((nns.GT8134028_12.24.36.48-GT8134028_12.test)^2)

# SSE 60
sum((nns.GT8134028_12.24.36.48.60-GT8134028_12.test)^2)

# SSE 72
sum((nns.GT8134028_12.24.36.48.60.72-GT8134028_12.test)^2)

# SSE 84
sum((nns.GT8134028_12.24.36.48.60.72.84-GT8134028_12.test)^2)
```

```{r data4a}
# Incorporate nonlinearity
nns.GT8134028_12=NNS.ARMA(GT8134028_12.train,h=24,seasonal.factor = 12,method='both', plot = FALSE)

# SSE 12
sum((nns.GT8134028_12-GT8134028_12.test)^2)

# Isolate nonlinearity
nns.GT8134028_12=NNS.ARMA(GT8134028_12.train,h=24,seasonal.factor = 12,method='nonlin', plot = FALSE)

# SSE 12
sum((nns.GT8134028_12-GT8134028_12.test)^2)
```

```{r data4full}
nns.GT8134028_12_12=NNS.ARMA(GT8134028,training.set=372,h=12,seasonal.factor = 12,method='both')

# SSE 12
sum((nns.GT8134028_12_12-tail(GT8134028,12))^2)

# NSE Statistic
NSE(nns.GT8134028_12_12,tail(GT8134028,12))
```

##4.2 24 Month Out of Sample Forecast
```{r data4_24}
# Create a training set
GT8134028_24.train=GT8134028[1:312]

# Create a test set
GT8134028_24.test=GT8134028[313:360]

nns.GT8134028_12=NNS.ARMA(GT8134028_24.train,h=48,seasonal.factor = 12,method='lin', plot = FALSE)

nns.GT8134028_12.24=NNS.ARMA(GT8134028_24.train,h=48,seasonal.factor = c(12,24),method='lin', plot = FALSE)

nns.GT8134028_12.24.36=NNS.ARMA(GT8134028_24.train,h=48,seasonal.factor = c(12,24,36),method='lin', plot = FALSE)

nns.GT8134028_12.24.36.48=NNS.ARMA(GT8134028_24.train,h=48,seasonal.factor = c(12,24,36,48),method='lin', plot = FALSE)

nns.GT8134028_12.24.36.48.60=NNS.ARMA(GT8134028_24.train,h=48,seasonal.factor = c(12,24,36,48,60),method='lin', plot = FALSE)

nns.GT8134028_12.24.36.48.60.72=NNS.ARMA(GT8134028_24.train,h=48,seasonal.factor = c(12,24,36,48,60,72),method='lin', plot = FALSE)


# SSE 12
sum((nns.GT8134028_12-GT8134028_24.test)^2)

# SSE 24
sum((nns.GT8134028_12.24-GT8134028_24.test)^2)

# SSE 36
sum((nns.GT8134028_12.24.36-GT8134028_24.test)^2)

# SSE 48
sum((nns.GT8134028_12.24.36.48-GT8134028_24.test)^2)

# SSE 60
sum((nns.GT8134028_12.24.36.48.60-GT8134028_24.test)^2)

# SSE 72
sum((nns.GT8134028_12.24.36.48.60.72-GT8134028_24.test)^2)


# Incorporate nonlinearity
nns.GT8134028_12=NNS.ARMA(GT8134028_24.train,h=48,seasonal.factor = 12,method='both', plot = FALSE)

# SSE 12 both
sum((nns.GT8134028_12-GT8134028_24.test)^2)

# Isolate nonlinearity
nns.GT8134028_12=NNS.ARMA(GT8134028_24.train,h=48,seasonal.factor = 12,method='nonlin', plot = FALSE)

# SSE 12 nonlin
sum((nns.GT8134028_12-GT8134028_24.test)^2)

```

```{r data4_24b}
nns.GT8134028_12_24=NNS.ARMA(GT8134028,h=24,training.set = 360,seasonal.factor = 12,method='both')

# SSE 12
sum((nns.GT8134028_12_24-tail(GT8134028,24))^2)

# NSE Statistic
NSE(nns.GT8134028_12_24,tail(GT8134028,24))
```



#5. Forecasts for `GT8153030`
View our data.
```{r plots5}
plot(GT8153030,type='l')
```

##5.1 12 Month Out of Sample Forecast
```{r data5}
# Create a training set
GT8153030_12.train=GT8153030[1:348]

# Create a test set
GT8153030_12.test=GT8153030[349:372]

nns.GT8153030_12=NNS.ARMA(GT8153030_12.train,h=24,seasonal.factor = 12,method='lin', plot = FALSE)

nns.GT8153030_12.24=NNS.ARMA(GT8153030_12.train,h=24,seasonal.factor = c(12,24),method='lin', plot = FALSE)

nns.GT8153030_12.24.36=NNS.ARMA(GT8153030_12.train,h=24,seasonal.factor = c(12,24,36),method='lin', plot = FALSE)

nns.GT8153030_12.24.36.48=NNS.ARMA(GT8153030_12.train,h=24,seasonal.factor = c(12,24,36,48),method='lin', plot = FALSE)

nns.GT8153030_12.24.36.48.60=NNS.ARMA(GT8153030_12.train,h=24,seasonal.factor = c(12,24,36,48,60),method='lin', plot = FALSE)

nns.GT8153030_12.24.36.48.60.72=NNS.ARMA(GT8153030_12.train,h=24,seasonal.factor = c(12,24,36,48,60,72),method='lin', plot = FALSE)

nns.GT8153030_12.24.36.48.60.72.84=NNS.ARMA(GT8153030_12.train,h=24,seasonal.factor = c(12,24,36,48,60,72,84),method='lin', plot = FALSE)

# SSE 12
sum((nns.GT8153030_12-GT8153030_12.test)^2)

# SSE 24
sum((nns.GT8153030_12.24-GT8153030_12.test)^2)

# SSE 36
sum((nns.GT8153030_12.24.36-GT8153030_12.test)^2)

# SSE 48
sum((nns.GT8153030_12.24.36.48-GT8153030_12.test)^2)

# SSE 60
sum((nns.GT8153030_12.24.36.48.60-GT8153030_12.test)^2)

# SSE 72
sum((nns.GT8153030_12.24.36.48.60.72-GT8153030_12.test)^2)

# SSE 84
sum((nns.GT8153030_12.24.36.48.60.72.84-GT8153030_12.test)^2)
```

```{r data5a}
# Incorporate nonlinearity
nns.GT8153030_12=NNS.ARMA(GT8153030_12.train,h=24,seasonal.factor = 12,method='both', plot = FALSE)

# SSE 12
sum((nns.GT8153030_12-GT8153030_12.test)^2)

# Isolate nonlinearity
nns.GT8153030_12=NNS.ARMA(GT8153030_12.train,h=24,seasonal.factor = 12,method='nonlin', plot = FALSE)

# SSE 12
sum((nns.GT8153030_12-GT8153030_12.test)^2)
```

```{r data5full}
nns.GT8153030_12_12=NNS.ARMA(GT8153030,training.set=372,h=12,seasonal.factor = 12,method='both')

# SSE 12
sum((nns.GT8153030_12_12-tail(GT8153030,12))^2)

# NSE Statistic
NSE(nns.GT8153030_12_12,tail(GT8153030,12))
```

##5.2 24 Month Out of Sample Forecast
```{r data5_24}
# Create a training set
GT8153030_24.train=GT8153030[1:312]

# Create a test set
GT8153030_24.test=GT8153030[313:360]

nns.GT8153030_12=NNS.ARMA(GT8153030_24.train,h=48,seasonal.factor = 12,method='lin', plot = FALSE)

nns.GT8153030_12.24=NNS.ARMA(GT8153030_24.train,h=48,seasonal.factor = c(12,24),method='lin', plot = FALSE)

nns.GT8153030_12.24.36=NNS.ARMA(GT8153030_24.train,h=48,seasonal.factor = c(12,24,36),method='lin', plot = FALSE)

nns.GT8153030_12.24.36.48=NNS.ARMA(GT8153030_24.train,h=48,seasonal.factor = c(12,24,36,48),method='lin', plot = FALSE)

nns.GT8153030_12.24.36.48.60=NNS.ARMA(GT8153030_24.train,h=48,seasonal.factor = c(12,24,36,48,60),method='lin', plot = FALSE)

nns.GT8153030_12.24.36.48.60.72=NNS.ARMA(GT8153030_24.train,h=48,seasonal.factor = c(12,24,36,48,60,72),method='lin', plot = FALSE)


# SSE 12
sum((nns.GT8153030_12-GT8153030_24.test)^2)

# SSE 24
sum((nns.GT8153030_12.24-GT8153030_24.test)^2)

# SSE 36
sum((nns.GT8153030_12.24.36-GT8153030_24.test)^2)

# SSE 48
sum((nns.GT8153030_12.24.36.48-GT8153030_24.test)^2)

# SSE 60
sum((nns.GT8153030_12.24.36.48.60-GT8153030_24.test)^2)

# SSE 72
sum((nns.GT8153030_12.24.36.48.60.72-GT8153030_24.test)^2)


# Incorporate nonlinearity
nns.GT8153030_12.24.36.48.60=NNS.ARMA(GT8153030_24.train,h=48,seasonal.factor = c(12,24,36,48,60),method='both', plot = FALSE)

# SSE 60 both
sum((nns.GT8153030_12.24.36.48.60-GT8153030_24.test)^2)

# Isolate nonlinearity
nns.GT8153030_12.24.36.48.60=NNS.ARMA(GT8153030_24.train,h=48,seasonal.factor = c(12,24,36,48,60),method='nonlin', plot = FALSE)

# SSE 60 nonlin
sum((nns.GT8153030_12.24.36.48.60-GT8153030_24.test)^2)
```

```{r data5_24b}
nns.GT8153030_12.24.36.48.60_24=NNS.ARMA(GT8153030,h=24,training.set = 360,seasonal.factor = c(12,24,36,48,60),method='nonlin')

# SSE 60
sum((nns.GT8153030_12.24.36.48.60_24-tail(GT8153030,24))^2)

# NSE Statistic
NSE(nns.GT8153030_12.24.36.48.60_24,tail(GT8153030,24))
```




#6. Forecasts for `GT8153031`
View our data.
```{r plots6}
plot(GT8153031,type='l')
```

##6.1 12 Month Out of Sample Forecast
```{r data6}
# Create a training set
GT8153031_12.train=GT8153031[1:348]

# Create a test set
GT8153031_12.test=GT8153031[349:372]

nns.GT8153031_12=NNS.ARMA(GT8153031_12.train,h=24,seasonal.factor = 12,method='lin', plot = FALSE)

nns.GT8153031_12.24=NNS.ARMA(GT8153031_12.train,h=24,seasonal.factor = c(12,24),method='lin', plot = FALSE)

nns.GT8153031_12.24.36=NNS.ARMA(GT8153031_12.train,h=24,seasonal.factor = c(12,24,36),method='lin', plot = FALSE)

nns.GT8153031_12.24.36.48=NNS.ARMA(GT8153031_12.train,h=24,seasonal.factor = c(12,24,36,48),method='lin', plot = FALSE)

nns.GT8153031_12.24.36.48.60=NNS.ARMA(GT8153031_12.train,h=24,seasonal.factor = c(12,24,36,48,60),method='lin', plot = FALSE)

nns.GT8153031_12.24.36.48.60.72=NNS.ARMA(GT8153031_12.train,h=24,seasonal.factor = c(12,24,36,48,60,72),method='lin', plot = FALSE)

nns.GT8153031_12.24.36.48.60.72.84=NNS.ARMA(GT8153031_12.train,h=24,seasonal.factor = c(12,24,36,48,60,72,84),method='lin', plot = FALSE)

# SSE 12
sum((nns.GT8153031_12-GT8153031_12.test)^2)

# SSE 24
sum((nns.GT8153031_12.24-GT8153031_12.test)^2)

# SSE 36
sum((nns.GT8153031_12.24.36-GT8153031_12.test)^2)

# SSE 48
sum((nns.GT8153031_12.24.36.48-GT8153031_12.test)^2)

# SSE 60
sum((nns.GT8153031_12.24.36.48.60-GT8153031_12.test)^2)

# SSE 72
sum((nns.GT8153031_12.24.36.48.60.72-GT8153031_12.test)^2)

# SSE 84
sum((nns.GT8153031_12.24.36.48.60.72.84-GT8153031_12.test)^2)
```

```{r data6a}
# Incorporate nonlinearity
nns.GT8153031_12=NNS.ARMA(GT8153031_12.train,h=24,seasonal.factor = 12,method='both', plot = FALSE)

# SSE 12
sum((nns.GT8153031_12-GT8153031_12.test)^2)

# Isolate nonlinearity
nns.GT8153031_12=NNS.ARMA(GT8153031_12.train,h=24,seasonal.factor = 12,method='nonlin', plot = FALSE)

# SSE 12
sum((nns.GT8153031_12-GT8153031_12.test)^2)
```

```{r data6full}
nns.GT8153031_12_12=NNS.ARMA(GT8153031,training.set=372,h=12,seasonal.factor = 12,method='both')

# SSE 12
sum((nns.GT8153031_12_12-tail(GT8153031,12))^2)

# NSE Statistic
NSE(nns.GT8153031_12_12,tail(GT8153031,12))
```

##6.2 24 Month Out of Sample Forecast
```{r data6_24}
# Create a training set
GT8153031_24.train=GT8153031[1:312]

# Create a test set
GT8153031_24.test=GT8153031[313:360]

nns.GT8153031_12=NNS.ARMA(GT8153031_24.train,h=48,seasonal.factor = 12,method='lin', plot = FALSE)

nns.GT8153031_12.24=NNS.ARMA(GT8153031_24.train,h=48,seasonal.factor = c(12,24),method='lin', plot = FALSE)

nns.GT8153031_12.24.36=NNS.ARMA(GT8153031_24.train,h=48,seasonal.factor = c(12,24,36),method='lin', plot = FALSE)

nns.GT8153031_12.24.36.48=NNS.ARMA(GT8153031_24.train,h=48,seasonal.factor = c(12,24,36,48),method='lin', plot = FALSE)

nns.GT8153031_12.24.36.48.60=NNS.ARMA(GT8153031_24.train,h=48,seasonal.factor = c(12,24,36,48,60),method='lin', plot = FALSE)

nns.GT8153031_12.24.36.48.60.72=NNS.ARMA(GT8153031_24.train,h=48,seasonal.factor = c(12,24,36,48,60,72),method='lin', plot = FALSE)


# SSE 12
sum((nns.GT8153031_12-GT8153031_24.test)^2)

# SSE 24
sum((nns.GT8153031_12.24-GT8153031_24.test)^2)

# SSE 36
sum((nns.GT8153031_12.24.36-GT8153031_24.test)^2)

# SSE 48
sum((nns.GT8153031_12.24.36.48-GT8153031_24.test)^2)

# SSE 60
sum((nns.GT8153031_12.24.36.48.60-GT8153031_24.test)^2)

# SSE 72
sum((nns.GT8153031_12.24.36.48.60.72-GT8153031_24.test)^2)


# Incorporate nonlinearity
nns.GT8153031_12.24.36.48.60=NNS.ARMA(GT8153031_24.train,h=48,seasonal.factor = c(12,24,36,48,60),method='both', plot = FALSE)

# SSE 60 both
sum((nns.GT8153031_12.24.36.48.60-GT8153031_24.test)^2)

# Isolate nonlinearity
nns.GT8153031_12.24.36.48.60=NNS.ARMA(GT8153031_24.train,h=48,seasonal.factor = c(12,24,36,48,60),method='nonlin', plot = FALSE)

# SSE 60 nonlin
sum((nns.GT8153031_12.24.36.48.60-GT8153031_24.test)^2)
```

```{r data6_24b}
nns.GT8153031_12.24.36.48.60_24=NNS.ARMA(GT8153031,h=24,training.set = 360,seasonal.factor = c(12,24,36,48,60),method='nonlin')

# SSE 60
sum((nns.GT8153031_12.24.36.48.60_24-tail(GT8153031,24))^2)

# NSE Statistic
NSE(nns.GT8153031_12.24.36.48.60_24,tail(GT8153031,24))
```


#7. Forecasts for `GT8172035`
View our data.
```{r plots7}
plot(GT8172035,type='l')
```

##7.1 12 Month Out of Sample Forecast
```{r data7}
# Create a training set
GT8172035_12.train=GT8172035[1:348]

# Create a test set
GT8172035_12.test=GT8172035[349:372]

nns.GT8172035_12=NNS.ARMA(GT8172035_12.train,h=24,seasonal.factor = 12,method='lin', plot = FALSE)

nns.GT8172035_12.24=NNS.ARMA(GT8172035_12.train,h=24,seasonal.factor = c(12,24),method='lin', plot = FALSE)

nns.GT8172035_12.24.36=NNS.ARMA(GT8172035_12.train,h=24,seasonal.factor = c(12,24,36),method='lin', plot = FALSE)

nns.GT8172035_12.24.36.48=NNS.ARMA(GT8172035_12.train,h=24,seasonal.factor = c(12,24,36,48),method='lin', plot = FALSE)

nns.GT8172035_12.24.36.48.60=NNS.ARMA(GT8172035_12.train,h=24,seasonal.factor = c(12,24,36,48,60),method='lin', plot = FALSE)

nns.GT8172035_12.24.36.48.60.72=NNS.ARMA(GT8172035_12.train,h=24,seasonal.factor = c(12,24,36,48,60,72),method='lin', plot = FALSE)

nns.GT8172035_12.24.36.48.60.72.84=NNS.ARMA(GT8172035_12.train,h=24,seasonal.factor = c(12,24,36,48,60,72,84),method='lin', plot = FALSE)

# SSE 12
sum((nns.GT8172035_12-GT8172035_12.test)^2)

# SSE 24
sum((nns.GT8172035_12.24-GT8172035_12.test)^2)

# SSE 36
sum((nns.GT8172035_12.24.36-GT8172035_12.test)^2)

# SSE 48
sum((nns.GT8172035_12.24.36.48-GT8172035_12.test)^2)

# SSE 60
sum((nns.GT8172035_12.24.36.48.60-GT8172035_12.test)^2)

# SSE 72
sum((nns.GT8172035_12.24.36.48.60.72-GT8172035_12.test)^2)

# SSE 84
sum((nns.GT8172035_12.24.36.48.60.72.84-GT8172035_12.test)^2)
```

```{r data7a}
# Incorporate nonlinearity
nns.GT8172035_12.24=NNS.ARMA(GT8172035_12.train,h=24,seasonal.factor = c(12,24),method='both', plot = FALSE)

# SSE 24
sum((nns.GT8172035_12.24-GT8172035_12.test)^2)

# Isolate nonlinearity
nns.GT8172035_12.24=NNS.ARMA(GT8172035_12.train,h=24,seasonal.factor = c(12,24),method='nonlin', plot = FALSE)

# SSE 24
sum((nns.GT8172035_12.24-GT8172035_12.test)^2)
```

```{r data7full}
nns.GT8172035_12_12=NNS.ARMA(GT8172035,training.set=372,h=12,seasonal.factor = c(12,24),method='both')

# SSE 24
sum((nns.GT8172035_12_12-tail(GT8172035,12))^2)

# NSE Statistic
NSE(nns.GT8172035_12_12,tail(GT8172035,12))
```

##7.2 24 Month Out of Sample Forecast
```{r data7_24}
# Create a training set
GT8172035_24.train=GT8172035[1:312]

# Create a test set
GT8172035_24.test=GT8172035[313:360]

nns.GT8172035_12=NNS.ARMA(GT8172035_24.train,h=48,seasonal.factor = 12,method='lin', plot = FALSE)

nns.GT8172035_12.24=NNS.ARMA(GT8172035_24.train,h=48,seasonal.factor = c(12,24),method='lin', plot = FALSE)

nns.GT8172035_12.24.36=NNS.ARMA(GT8172035_24.train,h=48,seasonal.factor = c(12,24,36),method='lin', plot = FALSE)

nns.GT8172035_12.24.36.48=NNS.ARMA(GT8172035_24.train,h=48,seasonal.factor = c(12,24,36,48),method='lin', plot = FALSE)

nns.GT8172035_12.24.36.48.60=NNS.ARMA(GT8172035_24.train,h=48,seasonal.factor = c(12,24,36,48,60),method='lin', plot = FALSE)

nns.GT8172035_12.24.36.48.60.72=NNS.ARMA(GT8172035_24.train,h=48,seasonal.factor = c(12,24,36,48,60,72),method='lin', plot = FALSE)


# SSE 12
sum((nns.GT8172035_12-GT8172035_24.test)^2)

# SSE 24
sum((nns.GT8172035_12.24-GT8172035_24.test)^2)

# SSE 36
sum((nns.GT8172035_12.24.36-GT8172035_24.test)^2)

# SSE 48
sum((nns.GT8172035_12.24.36.48-GT8172035_24.test)^2)

# SSE 60
sum((nns.GT8172035_12.24.36.48.60-GT8172035_24.test)^2)

# SSE 72
sum((nns.GT8172035_12.24.36.48.60.72-GT8172035_24.test)^2)


# Incorporate nonlinearity
nns.GT8172035_12.24.36.48.60=NNS.ARMA(GT8172035_24.train,h=48,seasonal.factor = c(12,24,36,48,60),method='both', plot = FALSE)

# SSE 60 both
sum((nns.GT8172035_12.24.36.48.60-GT8172035_24.test)^2)

# Isolate nonlinearity
nns.GT8172035_12.24.36.48.60=NNS.ARMA(GT8172035_24.train,h=48,seasonal.factor = c(12,24,36,48,60),method='nonlin', plot = FALSE)

# SSE 60 nonlin
sum((nns.GT8172035_12.24.36.48.60-GT8172035_24.test)^2)
```

```{r data7_24b}
nns.GT8172035_12.24.36.48.60_24=NNS.ARMA(GT8172035,h=24,training.set = 360,seasonal.factor = c(12,24,36,48,60),method='nonlin')

# SSE
sum((nns.GT8172035_12.24.36.48.60_24-tail(GT8172035,24))^2)

# NSE Statistic
NSE(nns.GT8172035_12.24.36.48.60_24,tail(GT8172035,24))
```


#8. Forecasts for `GT8172037`
View our data.
```{r plots8}
plot(GT8172037,type='l')
```

##8.1 12 Month Out of Sample Forecast
```{r data8}
# Create a training set
GT8172037_12.train=GT8172037[1:348]

# Create a test set
GT8172037_12.test=GT8172037[349:372]

nns.GT8172037_12=NNS.ARMA(GT8172037_12.train,h=24,seasonal.factor = 12,method='lin', plot = FALSE)

nns.GT8172037_12.24=NNS.ARMA(GT8172037_12.train,h=24,seasonal.factor = c(12,24),method='lin', plot = FALSE)

nns.GT8172037_12.24.36=NNS.ARMA(GT8172037_12.train,h=24,seasonal.factor = c(12,24,36),method='lin', plot = FALSE)

nns.GT8172037_12.24.36.48=NNS.ARMA(GT8172037_12.train,h=24,seasonal.factor = c(12,24,36,48),method='lin', plot = FALSE)

nns.GT8172037_12.24.36.48.60=NNS.ARMA(GT8172037_12.train,h=24,seasonal.factor = c(12,24,36,48,60),method='lin', plot = FALSE)

nns.GT8172037_12.24.36.48.60.72=NNS.ARMA(GT8172037_12.train,h=24,seasonal.factor = c(12,24,36,48,60,72),method='lin', plot = FALSE)

nns.GT8172037_12.24.36.48.60.72.84=NNS.ARMA(GT8172037_12.train,h=24,seasonal.factor = c(12,24,36,48,60,72,84),method='lin', plot = FALSE)

# SSE 12
sum((nns.GT8172037_12-GT8172037_12.test)^2)

# SSE 24
sum((nns.GT8172037_12.24-GT8172037_12.test)^2)

# SSE 36
sum((nns.GT8172037_12.24.36-GT8172037_12.test)^2)

# SSE 48
sum((nns.GT8172037_12.24.36.48-GT8172037_12.test)^2)

# SSE 60
sum((nns.GT8172037_12.24.36.48.60-GT8172037_12.test)^2)

# SSE 72
sum((nns.GT8172037_12.24.36.48.60.72-GT8172037_12.test)^2)

# SSE 84
sum((nns.GT8172037_12.24.36.48.60.72.84-GT8172037_12.test)^2)
```

```{r data8a}
# Incorporate nonlinearity
nns.GT8172037_12.24.36=NNS.ARMA(GT8172037_12.train,h=24,seasonal.factor = c(12,24,36),method='both', plot = FALSE)

# SSE 36
sum((nns.GT8172037_12.24.36-GT8172037_12.test)^2)

# Isolate nonlinearity
nns.GT8172037_12.24.36=NNS.ARMA(GT8172037_12.train,h=24,seasonal.factor = c(12,24,36),method='nonlin', plot = FALSE)

# SSE 36
sum((nns.GT8172037_12.24.36-GT8172037_12.test)^2)
```

```{r data8full}
nns.GT8172037_12.24.36_12=NNS.ARMA(GT8172037,training.set=372,h=12,seasonal.factor = c(12,24,36),method='both')

# SSE 36
sum((nns.GT8172037_12.24.36_12-tail(GT8172037,12))^2)

# NSE Statistic
NSE(nns.GT8172037_12.24.36_12,tail(GT8172037,12))
```

##8.2 24 Month Out of Sample Forecast
```{r data8_24}
# Create a training set
GT8172037_24.train=GT8172037[1:312]

# Create a test set
GT8172037_24.test=GT8172037[313:360]

nns.GT8172037_12=NNS.ARMA(GT8172037_24.train,h=48,seasonal.factor = 12,method='lin', plot = FALSE)

nns.GT8172037_12.24=NNS.ARMA(GT8172037_24.train,h=48,seasonal.factor = c(12,24),method='lin', plot = FALSE)

nns.GT8172037_12.24.36=NNS.ARMA(GT8172037_24.train,h=48,seasonal.factor = c(12,24,36),method='lin', plot = FALSE)

nns.GT8172037_12.24.36.48=NNS.ARMA(GT8172037_24.train,h=48,seasonal.factor = c(12,24,36,48),method='lin', plot = FALSE)

nns.GT8172037_12.24.36.48.60=NNS.ARMA(GT8172037_24.train,h=48,seasonal.factor = c(12,24,36,48,60),method='lin', plot = FALSE)

nns.GT8172037_12.24.36.48.60.72=NNS.ARMA(GT8172037_24.train,h=48,seasonal.factor = c(12,24,36,48,60,72),method='lin', plot = FALSE)


# SSE 12
sum((nns.GT8172037_12-GT8172037_24.test)^2)

# SSE 24
sum((nns.GT8172037_12.24-GT8172037_24.test)^2)

# SSE 36
sum((nns.GT8172037_12.24.36-GT8172037_24.test)^2)

# SSE 48
sum((nns.GT8172037_12.24.36.48-GT8172037_24.test)^2)

# SSE 60
sum((nns.GT8172037_12.24.36.48.60-GT8172037_24.test)^2)

# SSE 72
sum((nns.GT8172037_12.24.36.48.60.72-GT8172037_24.test)^2)


# Incorporate nonlinearity
nns.GT8172037_12.24.36.48.60=NNS.ARMA(GT8172037_24.train,h=48,seasonal.factor = c(12,24,36,48,60),method='both', plot = FALSE)

# SSE 60 both
sum((nns.GT8172037_12.24.36.48.60-GT8172037_24.test)^2)

# Isolate nonlinearity
nns.GT8172037_12.24.36.48.60=NNS.ARMA(GT8172037_24.train,h=48,seasonal.factor = c(12,24,36,48,60),method='nonlin', plot = FALSE)

# SSE 60 nonlin
sum((nns.GT8172037_12.24.36.48.60-GT8172037_24.test)^2)
```

```{r data8_24b}
nns.GT8172037_12.24.36.48.60_24=NNS.ARMA(GT8172037,h=24,training.set = 360,seasonal.factor = c(12,24,36,48,60),method='nonlin')

# SSE 60
sum((nns.GT8172037_12.24.36.48.60_24-tail(GT8172037,24))^2)

# NSE Statistic
NSE(nns.GT8172037_12.24.36.48.60_24,tail(GT8172037,24))
```


# Summary
```{r NSEs}
NSE.mtx=cbind(c(NSE(nns.GT8134017_12.24_12,tail(GT8134017,12)),
    NSE(nns.GT8134022_12.24_12,tail(GT8134022,12)),
    NSE(nns.GT8134027_12.24_12,tail(GT8134027,12)),
    NSE(nns.GT8134028_12_12,tail(GT8134028,12)),
    NSE(nns.GT8153030_12_12,tail(GT8153030,12)),
    NSE(nns.GT8153031_12_12,tail(GT8153031,12)),
    NSE(nns.GT8172035_12_12,tail(GT8172035,12)),
    NSE(nns.GT8172037_12.24.36_12,tail(GT8172037,12))
  ),
  c(NSE(nns.GT8134017_12.24.36.48.60.72_24,tail(GT8134017,24)),
   NSE(nns.GT8134022_12.24.36.48_24,tail(GT8134022,24)),
   NSE(nns.GT8134027_12.24.36.48.60_24,tail(GT8134027,24)),
   NSE(nns.GT8134028_12_24,tail(GT8134028,24)),
   NSE(nns.GT8153030_12.24.36.48.60_24,tail(GT8153030,24)),
   NSE(nns.GT8153031_12.24.36.48.60_24,tail(GT8153031,24)),
   NSE(nns.GT8172035_12.24.36.48.60_24,tail(GT8172035,24)),
   NSE(nns.GT8172037_12.24.36.48.60_24,tail(GT8172037,24)) 
  )
)

colnames(NSE.mtx)=c("12 month out of sample","24 month out of sample")

rownames(NSE.mtx)=c('GT8134017','GT8134022','GT8134027','GT8134028','GT8153030','GT8153031','GT8172035','GT8172037')

NSE.mtx
```

